Conservation of interaction partners between related plants varies widely across communities and between plant families - Supporting Information

### 2019-07-05 manuscript/supporting_info.tex
SI text ok, want to fix Fig. S2

    We repeated some of our analyses using the proportion of shared interaction partners as the response rather than a tuple describing the number of interaction partners that are shared and not shared. This approach is more common when performing logistic regressions, but loses information about the varying weights of evidence about different plant pairs. This lost information can limit the power of the regression to detect weak trends.

    Across all networks, more distantly-related plants remained less likely
    to share interaction partners, but this relationship was not significant 
    in herbivory networks ($\beta_{distance}$=-1.07, $p$=0.477; compare to 
    $\beta_{distance}$=-6.82, $p$\textless0.001 in the main text). Plants in pollination networks again tended to share fewer interaction partners overall ($\beta_{pollination}$=-0.881, $p$\textless0.001; compare to $
    beta_{pollination}$=-1.44, $p$\textless0.001 in the main text), and the decrease in overlap with increasing phylogenetic distance was steeper than in herbivory networks ($\beta_{distance:pollination}$=-26.8, $p$\textless0.001). Thus, while we observed the same trends when treating the response as a proportion and as a tuple, the tuple format displayed these trends more clearly. This is likely because of the additional informaion incorporated in the tuple.

@@

    \begin{figure}[!h]
        \begin{center}
          \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/proportion_regression_lines_full_color.eps}}
        \end{center}
         \caption{\small When considering niche overlap as the proportion of shared interaction partners rather than both the number of interaction partners that are shared and not shared, there is much less variability between networks. The overall trends observed are also much weaker than those detected when using all of the available information. Compare with Fig. 1, main text.
         }
        \label{within_family_regression}
      \end{figure}

@@

    \subsection*{Networks shown in each panel of Figure S1}

@@

    Models for nine families could not be fit because there was no variation in the phylogenetic distance between plants, their numbers of shared interaction partners, or both. These families were \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Cactaceae}, \emph{Cornaceae}, \emph{Gentianaceae}, \emph{Liliaceae}, \emph{Oxalidaceae}, \emph{Rhamnaceae}, and \emph{Zingiberaceae}. Further, we could not fit a model for \emph{Sapindaceae} in herbivory networks as all but one plant pair had the same phylogenetic distances.

@@

    We repeated some of our analyses using the proportion of shared interaction partners as the response rather than a tuple describing the number of interaction partners that are shared and not shared. This approach is more common when performing logistic regressions, but loses information about the varying weights of evidence about different plant pairs. This lost information can limit the power of the regression to detect weak trends.

    Across all networks, more distantly-related plants remained less likely
    to share interaction partners, but this relationship was not significant 
    in herbivory networks ($\beta_{distance}$=-1.07, $p$=0.477; compare to 
    $\beta_{distance}$=-6.82, $p$\textless0.001 in the main text). Plants in pollination networks again tended to share fewer interaction partners overall ($\beta_{pollination}$=-0.881, $p$\textless0.001; compare to $
    beta_{pollination}$=-1.44, $p$\textless0.001 in the main text), and the decrease in overlap with increasing phylogenetic distance was steeper than in herbivory networks ($\beta_{distance:pollination}$=-26.8, $p$\textless0.001). Thus, while we observed the same trends when treating the response as a proportion and as a tuple, the tuple format displayed these trends more clearly. This is likely because of the additional informaion incorporated in the tuple.

    Within networks, using the proportion of shared interaction partners rather than a tuple resulted in significant relationships between phylogenetic distance and overlap in interaction partners in five herbivory networks and seven pollination networks (compare to seven and 34 networks, respectively, in the main text). In each case, the proportion of shared interaction partners decreased with increasing phylogenetic distance. Again, this demonstrates the greater power of a Jaccard regression with a tuple response to capture weak trends. Notably, the single pollination network where overlap of interaction partners significantly \emph{increased} with increasing phylogenetic distance was not detected when using the proportion of shared interaction partners as a response.

>>>>

    We repeated some of our analyses using the proportion of shared interaction partners as the response rather than a tuple describing the number of interaction partners that are shared and not shared. This approach is common when performing logistic regressions, but loses information about the varying weights of evidence about different plant pairs. This lost information can limit the power of the regression to detect weak trends.

    Across all networks, more distantly-related plants remained less likely
    to share interaction partners, but this relationship was not significant 
    in herbivory networks ($\beta_{distance}$=-1.07, $p$=0.477; compare to 
    $\beta_{distance}$=-6.82, $p$\textless0.001 in the main text). Plants in pollination networks again tended to share fewer interaction partners overall ($\beta_{pollination}$=-0.881, $p$\textless0.001; compare to $
    \beta_{pollination}$=-1.44, $p$\textless0.001 in the main text), and the decrease in overlap with increasing phylogenetic distance was steeper than in herbivory networks ($\beta_{distance:pollination}$=-26.8, $p$\textless0.001; compare to $\beta_{distance:pollination}$=-18.5, $p$\textless0.001 in the main text). Thus, while we observed the same trends when treating the response as a proportion and as a tuple, the tuple format displayed these trends more clearly. This is likely because of the additional informaion incorporated in the tuple.

@@

    \begin{figure}[!h]
        \begin{center}
          \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/proportion_regression_lines_full_color.eps}}
        \end{center}
         \caption{\small When considering niche overlap as the proportion of shared interaction partners rather than both the number of interaction partners that are shared and not shared, there is much less variability between networks. The overall trends (thicker, darker lines) observed are also much weaker than those detected when using all of the available information. Compare with Fig. 1, main text. Both figures are plotted on the same scale.
         }
        \label{lineplot}
      \end{figure}

@@

    \subsection*{Networks shown in each panel of Figure S2}

@@

    Models for nine families could not be fit because there was no variation in the phylogenetic distance between plants, their numbers of shared interaction partners, or both. These families were \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Cactaceae}, \emph{Cornaceae}, \emph{Gentianaceae}, \emph{Liliaceae}, \emph{Oxalidaceae}, \emph{Rhamnaceae}, and \emph{Zingiberaceae}. Further, we could not fit a model for \emph{Lauraceae} in pollination networks or \emph{Sapindaceae} in herbivory or pollination networks as only one plant pair in each network type shared any interaction partners.

@@
